---
title: "Gene Dependency for Cancers, Week 1, Cooper's Team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls()) #clear everything
```

```{r}
# DO NOT ALTER ANY OF THIS BESIDES ADDING PACKAGES TO WORK WITH
# ONLY NEED TO RUN THIS ONCE

# installing necessary packages
library(plyr)
library(dplyr)
library(tidyverse)
library(taigr)
library(edgeR)

install.packages("pheatmap")
library(pheatmap)

metadata = load.from.taiga(data.name='public-21q1-4b39', 
                           data.version=33, 
                           data.file='sample_info', 
                           quiet = T)

mutation = load.from.taiga(data.name = 'public-21q1-4b39',
                            data.version = 33,
                            data.file = 'CCLE_mutations',
                            quiet = T)

expression =  load.from.taiga(data.name='public-21q1-4b39',
                             data.version=33,
                             data.file='CCLE_expression',
                             quiet = T)
colnames(expression) = stringr::word(colnames(expression), 1) 
expression = as.data.frame(expression)
expression$DepMap_ID = rownames(expression)

dependency = load.from.taiga(data.name='public-21q1-4b39',
                              data.version=33,
                              data.file='CRISPR_gene_effect',
                              quiet = T)
colnames(dependency) = stringr::word(colnames(dependency), 1) 
colnames(dependency) = paste(colnames(dependency), "_Dep", sep = "")
colnames(dependency)[colnames(dependency) == "DepMap_ID_Dep"] = "DepMap_ID"
dependency = as.data.frame(dependency)
dependency$DepMap_ID = rownames(dependency)

```

```{r}
# GETTING MOST FREQUENT CANCERS

table(metadata$primary_disease)
cancerCounts = as.data.frame(table(metadata$primary_disease))
cancerCounts = cancerCounts[cancerCounts$Var1 != "Unknown" ,]
cancerCounts # column 1: name of cancer
             # column 2: frequency of said cancer

ggplot(cancerCounts,  aes(x = reorder(Var1, -Freq), y = Freq))+ geom_bar(stat = "identity") + ggtitle("Frequency of Cancers in CCLE data") + labs(y= "Cancer Frequency", x = "Cancer Types") + theme(axis.text.x = element_text(angle = 90))
# removes cancers that were categorized as "Unknown."

```

```{r}
# select for top 15 most prevalent cancers in CCLE

top15Cancers = head(arrange(cancerCounts,-Freq), n = 15)

ggplot(top15Cancers,  aes(x = reorder(Var1, -Freq), y = Freq))+ geom_bar(stat = "identity") + ggtitle("Frequency of top 15 Cancers in CCLE data") + labs(y= "Cancer Frequency", x = "Cancer Types") + theme(axis.text.x = element_text(angle = 90))

```

```{r}
# Importing Cooper's MDD Data
library(readxl)
FinalList_2_ <- read_excel("~/Downloads/NEW_MDD_GeneLIST.xlsx")

colnames(FinalList_2_) = c("Gene", "FoldChange", "p-value") # rename to new dataset

#subset to those with an adjusted p-value of 0.00001 or less
MDDgenes = FinalList_2_[FinalList_2_$`p-value` < 0.00001, ]
MDDgenes = na.omit(MDDgenes) # remove values of NA

```


```{r}
# create new dependency dataset
justCancers = metadata[ , c("DepMap_ID", "primary_disease")]

DepMap_ID = dependency[,0]
dependency2 = data.frame(cbind(dependency,DepMap_ID))
CancerDependencies = inner_join(dependency, justCancers, "DepMap_ID")

colnames(top15Cancers) = c("primary_disease", "Freq")
Top15Dependencies = inner_join(CancerDependencies, top15Cancers, "primary_disease") # get dependencies of top 15 cancers 
```

```{r}
#Subset dependencies by the genes in the MDD dataframe
MDDgenes$Gene
x = MDDgenes$Gene
x = paste0(x, "_Dep")
intersect = intersect(x, colnames(dependency))
MDD_dependencies = dependency[, intersect]

#Full Joining MDD_dependencies_wDepMap with the just cancers then getting rid of the NAs
MDD_dependencies = cbind(data.frame(rownames(MDD_dependencies)), MDD_dependencies)
colnames(MDD_dependencies)[1] = "DepMap_ID"

#Combining the dataframes between the MDD gene dependencies and the Top 15 cancer dependencies
DepMap_ID = rownames(MDD_dependencies)
MDD_dependencies2 = data.frame(cbind(MDD_dependencies,DepMap_ID))
CombinedDependencies = inner_join(Top15Dependencies,MDD_dependencies2, "DepMap_ID")
```

```{r}
#Identifying the association values for MDD Genes
# DO NOT CHANGE ANYTHING, IT GETS FINICKY
colnames(expression)
y = MDDgenes$Gene
intersect2 = intersect(y, colnames(expression))
MDDExpression = expression[, intersect2]

DepMap_ID = rownames(MDDExpression)

MDDExpression = data.frame(cbind(MDDExpression,DepMap_ID))
MDDExpression = inner_join(MDDExpression, justCancers, "DepMap_ID")

MDDgenes = na.omit(MDDgenes)
FoldChange = MDDgenes$FoldChange
FoldChange = as.vector(FoldChange)

for (i in 1:length(FoldChange)){ 
  FoldChange[i] = 2^FoldChange[i] # de-logs the MDD genes
}

for (i in 1:length(FoldChange)){ 
  if ( FoldChange[i] > 1){
  print(FoldChange[i]);
}else if(FoldChange[i] < 1) {
   print(-FoldChange[i]^-1)
  FoldChange[i] = -FoldChange[i]^-1
  }
} #returns modified FoldChange into linear multiplication value

FoldChange_df = data.frame(FoldChange)
Gene = MDDgenes$Gene
Gene = na.omit(Gene)
Gene = data.frame(Gene)
Gene_FoldChange = cbind(FoldChange_df, Gene)
Gene_FoldChange
```


```{r}
#Rename from "gene" to "Gene"
gene = Gene_FoldChange$Gene
gene = paste0(gene, "_Dep")
gene
Gene_FoldChange1 = cbind(Gene_FoldChange, gene)
Gene_FoldChange1 = select(Gene_FoldChange1,-c("Gene")) 

# For each column grab the gene name
# Transformed FC for gene name 
# Multiply column for Transformed FC

getCorrelationValues = function(GeneName_Dep){
  
  for(i in colnames(MDD_dependencies2)){
    
    if(i == GeneName_Dep){ # loops through gene names and finds the one that matches the FoldChange score
      
      correlationVector = MDD_dependencies2[, i] * Gene_FoldChange1[Gene_FoldChange1$gene == GeneName_Dep, 1]
      return(correlationVector) # return the multiplied column
      
    }
    
  }
  
}

# running through all the genes
# final dataframe contains all the correlation values we want to work with
correlationDataframe = data.frame(getCorrelationValues("RETN_Dep")) 
colnames(correlationDataframe)[1] = "RETN_Dep"

for(i in Gene_FoldChange1$gene[2:length(Gene_FoldChange1$gene)]){
  
  testVector = getCorrelationValues(i)
  
  if(length(testVector) > 0){
    
    correlationDataframe = cbind(correlationDataframe, testVector)
    colnames(correlationDataframe)[length(correlationDataframe)] = i
    
  }
  
}

rownames(correlationDataframe) = rownames(MDD_dependencies2) # update rownames to be relevant DepMap cell line names

```

```{r}
# Getting Outliers of each Cancer Type

# function to get relevant cell lines by cell type
subsetByCancer = function(df, cancerName){
  
  allRelevantCells = metadata[metadata$primary_disease == cancerName, 1]
  return_df = data.frame()
  for(i in allRelevantCells){
    
    if(i %in% rownames(df)){
      
      return_df = rbind(return_df, df[c(i), ])
      
    } 
    
  }
  
  return(return_df)
  
}

# function to get the outliers of any given dataset
getOutliers = function(dep_df, cancerType){
  
  dep_df_median = apply(dep_df, 2, median)
  dep_df_median_df = data.frame(dep_df_median)
  dep_df_median_df = na.omit(dep_df_median_df)
  
  outliers = dep_df_median_df[dep_df_median_df$dep_df_median < -0.5 | dep_df_median_df$dep_df_median > 0.5, ]
  outliers_df = data.frame(outliers)
  
  geneNames = rownames(dep_df_median_df)[dep_df_median_df$dep_df_median < -0.5 | dep_df_median_df$dep_df_median > 0.5]
  outliers_df = cbind(geneNames, outliers_df)
  
  colnames(outliers_df) = c(cat(cancerType, "Gene Name"), cat(cancerType, "Dependency"))
  
  return(outliers_df)
  
}

# loop to return all of this in a new dataframe
outliers_df = data.frame()

for(i in top15Cancers[,1]){
  
  subset = subsetByCancer(correlationDataframe, i) # subset to relevant cancer
  outliers = getOutliers(subset, i)
  outliers = as.data.frame(t(outliers)) # get outliers of the specific cancer
  
  outliers_df = rbind.fill(outliers_df, outliers) 
  
}

outliers_df = as.data.frame(t(outliers_df)) # return list of outliers

# adding column names to the outliers dataframe

outliers_df_names = character(30)

for(i in 1:15){
  
  outliers_df_names[2*i - 1] = paste(top15Cancers[i,1], "Gene Name")
  outliers_df_names[2*i] = paste(top15Cancers[i,1], "Dependency")
  
} 

colnames(outliers_df) = c(outliers_df_names) # set names
# this dataframe contains outliers of all cancers
# odd numbered columns are gene names f a cancer
# even numbered columns are correlation scores of that cancer
# columns proceed in most preevalent to 15th most prevalen canceer

```

```{r}

# function to get t.test results from pair of cancer types for a specific geene

getT_Test = function(cancerType1, cancerType2, geneName){
  
  cancer1_df = subsetByCancer(correlationDataframe, cancerType1)
  cancer1_df = cancer1_df[, c(geneName)]
  
  cancer2_df = subsetByCancer(correlationDataframe, cancerType2)
  cancer2_df = cancer2_df[, c(geneName)]
  
  testResult = t.test(cancer1_df, cancer2_df)
  return(testResult)
  
  #DO NOT TOUCH ANY OF THIS IT WILL BREAK AND I DON'T KNOW WHY >:(
  
}

# function to get t.test results from pair of cancer types for all genes
getT_Test_all = function(cancerType1, cancerType2){
  
  cancer1_df = subsetByCancer(correlationDataframe, cancerType1)
  cancer2_df = subsetByCancer(correlationDataframe, cancerType2)
  
  testResult = t.test(cancer1_df, cancer2_df)
  return(testResult)
  
}

```

```{r}
# Compare non-outlier correlation data between cancers

# function to remove outliers from each cancer type
removedOutliers = function(cancerType){
  
  subset = subsetByCancer(correlationDataframe, cancerType)
  relevantOutliers = getOutliers(subset, cancerType)
  
  returnSubsetNames = colnames(subset)
  
  for(i in relevantOutliers[ , 1]){
    
    if(i %in% colnames(returnSubsetNames)){
      
      returnSubsetNames = subset(returnSubsetNames, colnames(returnSubsetNames) != i)
      
    }
    
  }
  
  return_df = subset[ , c(returnSubsetNames)]
  return(return_df)
  
}

# function gets t.test for data where the outlier is removed
# unused as of now
getT_Test_nonOutliers = function(cancerType1, cancerType2){
  
  cancer1_df = removedOutliers(cancerType1)
  cancer2_df = removedOutliers(cancerType2)
  
  testResult = t.test(cancer1_df, cancer2_df)
  return(testResult)
  
}

# Compare non-outlier correlation data between cancers
getComp_df = function(cancerType1, cancerType2){
  
  testResult = getT_Test_nonOutliers(top15Cancers[i, 1], top15Cancers[j, 1])
      
  comp_pval = testResult[['p.value']]
      
  comp_confTF = (testResult[['conf.int']][1] < 0) & (testResult[['conf.int']][2] > 0)
  comp_confTF = !comp_confTF # sees if the interval contains 0
                              # False means tha it is not significant
      
  meanDiff = abs(testResult[['estimate']][1] - testResult[['estimate']][2]) # gets difference of meaens
      
  if(testResult[['p.value']] < 0 & comp_confTF){ 
    # check if difference of means is both significant AND confidence interval does not contain zero
        
      checklist = TRUE
      comp_matVal = meanDiff
        
  } else{
    
    checklist = FALSE
    comp_matVal = -1 # a set value of -1 means it's insignificant
    
  }
  
  returnList = list("pval" = comp_pval, "confTF" = comp_confTF, "meanDiff" = meanDiff, "check" = checklist, "comp_matVal" = comp_matVal) # returns lis where you can use useful information afer it ges called
  return(returnList)
  
}

# run comparison function 

# set up all the dataframes containing comparisons between cancers
comp_df_pval = data.frame(matrix(NA, nrow = 15, ncol = 15))
comp_df_confTF = data.frame(matrix(NA, nrow = 15, ncol = 15))
comp_meanDiff_df = data.frame(matrix(NA, nrow = 15, ncol = 15))
comp_checklist = data.frame(matrix(NA, nrow = 15, ncol = 15))
comp_matrix = data.frame(matrix(NA, nrow = 15, ncol = 15))
   
# set up column and row names to match associated cancers
rownames(comp_df_pval) = c(top15Cancers[, 1])
colnames(comp_df_pval) = c(top15Cancers[, 1])
  
rownames(comp_df_confTF) = c(top15Cancers[, 1])
colnames(comp_df_confTF) = c(top15Cancers[, 1])
  
rownames(comp_meanDiff_df) = c(top15Cancers[, 1])
colnames(comp_meanDiff_df) = c(top15Cancers[, 1])
  
rownames(comp_checklist) = c(top15Cancers[, 1])
colnames(comp_checklist) = c(top15Cancers[, 1])

rownames(comp_matrix) = c(top15Cancers[, 1])
colnames(comp_matrix) = c(top15Cancers[, 1])
    
# run function for every pair of cancers
for(i in 2:15){
  
  for(j in 1:(i-1)){
    
    comp_df = getComp_df(top15Cancers[i, 1], top15Cancers[j, 1])
    
    comp_df_pval[j, i] = comp_df$pval
    comp_df_confTF[j, i] = comp_df$confTF
    comp_meanDiff_df[j, i] = comp_df$meanDiff
    comp_checklist[j, i] = comp_df$check
    comp_matrix[j, i] = comp_df$comp_matVal
    
  }
  
}

# plot  where 95-confidence interval AND p < 0.05 green, with bigger means greener. Ones that aren't satisfieed    are plotted blank
#!NOTE: THIS FUNCTION WAS NOT RAN BECAUSE ALL VALUES CAME BACK -1 
# IN OTHER WORDS, THERE WERE NO STATISTICALLY SIGNIFICANT DIFFERENCES FOUND BETWEEN CANCER DEPENDENCY VALUES
getComp_plot = function(cancerType1, cancerType2){
  
  #!TODO: finish the plotting!
  
}

```

```{r}
# Compare outlier correlation data between cancers
getOutlierComp_df = function(geneName){
  
  # similar data set up
  
  outlierComp_df_pval = data.frame(matrix(NA, nrow = 15, ncol = 15))
  outlierComp_df_confTF = data.frame(matrix(NA, nrow = 15, ncol = 15))
  meanDiff_df = data.frame(matrix(NA, nrow = 15, ncol = 15))
  checklist = data.frame(matrix(NA, nrow = 15, ncol = 15))
  outlierComp_matrix = data.frame(matrix(NA, nrow = 15, ncol = 15))
  
  rownames(outlierComp_df_pval) = c(top15Cancers[, 1])
  colnames(outlierComp_df_pval) = c(top15Cancers[, 1])
  
  rownames(outlierComp_df_confTF) = c(top15Cancers[, 1])
  colnames(outlierComp_df_confTF) = c(top15Cancers[, 1])
  
  rownames(meanDiff_df) = c(top15Cancers[, 1])
  colnames(meanDiff_df) = c(top15Cancers[, 1])
  
  rownames(checklist) = c(top15Cancers[, 1])
  colnames(checklist) = c(top15Cancers[, 1])
  
  rownames(outlierComp_matrix) = c(top15Cancers[, 1])
  colnames(outlierComp_matrix) = c(top15Cancers[, 1])
  
  # DO NOT TOUCH ANYTHING BELOW, IT GETS FUNKY
  # YOU GET AN ERROR WHEN i = 15 BECAUSE THERE IS ONLY 1 FIBROBLAST CELL LINE IN THE DATAFRAME WHICH BREAKS THE T        TEST
  
  # conceptually is identifical to above loop that looks similar
  for(i in 2:15){
  
    for(j in 1:(i-1)){
    
      testResult = getT_Test(as.matrix(top15Cancers)[i, 1], as.matrix(top15Cancers)[j, 1], geneName)
      
      outlierComp_df_pval[j, i] = testResult[['p.value']]
      
      outlierComp_df_confTF[j, i] = (testResult[['conf.int']][1] < 0) & (testResult[['conf.int']][2] > 0)
      outlierComp_df_confTF[j, i] = !outlierComp_df_confTF[j, i]
      
      meanDiff_df[j, i] = abs(testResult[['estimate']][1] - testResult[['estimate']][2])
      
      if(testResult[['p.value']] < 0 & outlierComp_df_confTF[j, i]){
        
        checklist[j, i] = TRUE
        outlierComp_matrix[j, i] = meanDiff_df[j, i]
        
      } else{
        
        checklist[j, i] = FALSE
        outlierComp_matrix[j, i] = -1
        
      }
    
    }
  
  }
  
  returnList = list("pval" = outlierComp_df_pval, "confTF" = outlierComp_df_confTF, "meanDiff" = meanDiff_df, "checklist" = checklist, "Heatmap_Matrix"= outlierComp_matrix) # return similar list to above code
  return(returnList)
  
}

# plot  where 95-confidence interval AND p < 0.05 green, with bigger means greener. Ones that aren't satisfieed    are plotted blank/another color
getOutlierComp_plot = function(geneName){
  
  outlierComp_matrix = getOutlierComp_df(geneName)[['Heatmap_Matrix']]
  pheatmap(outlierComp_matrix)
  
}

# run comparison function 

# get only the outliers genes to run with
genesOnly = as.matrix(outliers_df[, 1])
for (i in 2:15){
  
  genesOnly = rbind(genesOnly, as.matrix(outliers_df[, 2*i - 1]))
  
}

# remove NAs and duplicates
genesOnly = na.omit(genesOnly)

genesOnly = data.frame(genesOnly)
genesOnly = distinct(genesOnly) 
genesOnly = as.matrix(genesOnly)

# run through all genes and cancer pairs
for(geneName in genesOnly){
  
  outlierComp_df_pval = data.frame(matrix(NA, nrow = 15, ncol = 15))
  outlierComp_df_confTF = data.frame(matrix(NA, nrow = 15, ncol = 15))
  meanDiff_df = data.frame(matrix(NA, nrow = 15, ncol = 15))
  checklist = data.frame(matrix(NA, nrow = 15, ncol = 15))
  outlierComp_matrix = data.frame(matrix(NA, nrow = 15, ncol = 15))
  
  rownames(outlierComp_df_pval) = c(top15Cancers[, 1])
  colnames(outlierComp_df_pval) = c(top15Cancers[, 1])
  
  rownames(outlierComp_df_confTF) = c(top15Cancers[, 1])
  colnames(outlierComp_df_confTF) = c(top15Cancers[, 1])
  
  rownames(meanDiff_df) = c(top15Cancers[, 1])
  colnames(meanDiff_df) = c(top15Cancers[, 1])
  
  rownames(checklist) = c(top15Cancers[, 1])
  colnames(checklist) = c(top15Cancers[, 1])
  
  rownames(outlierComp_matrix) = c(top15Cancers[, 1])
  colnames(outlierComp_matrix) = c(top15Cancers[, 1])
  
  for(i in 2:15){
  
    for(j in 1:(i-1)){
    
      testResult = getT_Test(as.matrix(top15Cancers)[i, 1], as.matrix(top15Cancers)[j, 1], geneName)
      
      outlierComp_df_pval[j, i] = testResult[['p.value']]
      
      outlierComp_df_confTF[j, i] = (testResult[['conf.int']][1] < 0) & (testResult[['conf.int']][2] > 0)
      outlierComp_df_confTF[j, i] = !outlierComp_df_confTF[j, i]
      
      meanDiff_df[j, i] = abs(testResult[['estimate']][1] - testResult[['estimate']][2])
      
      if(testResult[['p.value']] < 0 & outlierComp_df_confTF[j, i]){
        
        checklist[j, i] = TRUE
        outlierComp_matrix[j, i] = meanDiff_df[j, i]
        
      } else{
        
        checklist[j, i] = FALSE
        outlierComp_matrix[j, i] = -1
        
      }
    
    }
    
  }
  
  # loop through to find if any gene was found to have non- -1 values in the matVal dataframes
  for(m in 1:15){
    
    for(n in 1:15){
      
      testVal = outlierComp_matrix[m, n]
      if(testVal != -1 & !is.na(testVal)){
        
        print(geneName)
        
      }
      
    }
    
  }
  
  #!NOTE: FOUND NO STATISTICALLY SIGNIFICANT CORRELATIONS FOR OUTLIER GENES BETWEEN ANY 2 CANCERS
  
}

```



```{r}
# plotting heatmaps for visualizing data
correlation_hm = as.matrix(correlationDataframe)

# look at only outlier genes
for(i in genesOnly){
    
  if(i %in% colnames(correlationDataframe)){
      
      correlation_hm = correlation_hm[, colnames(correlation_hm) != i]
      
  }
    
}
#!TODO: could be future visualization project (working with just outliers)

# get heatmaps for each cancer
for(i in top15Cancers$primary_disease){
  
  pheatmap(subsetByCancer(correlation_hm, i), cluster_rows = FALSE, cluster_cols = FALSE)
  
}

```

```{r}
# geting Outlier expression  data

getOutlier_exp = function(cancerType, geneName){ # returns MEAN of cancer expression
  
  relevantCells = metadata[metadata$primary_disease == cancerType, 1]
  relevantCells = intersect(relevantCells, rownames(expression))
  
  relevantCells_exp = subset(expression, rownames(expression) %in% relevantCells)
  relevantCells_exp = relevantCells_exp[, c(geneName)]
  
  returnList = list("mean" = mean(relevantCells_exp), "data" = relevantCells_exp) 
  
  return(returnList)
  
}

outliers_exp_df = data.frame(matrix(NA, nrow = 15, ncol = 30))
# getting column names

for(i in 1:15){
  
  cancerType = toString(top15Cancers[i, 1])
  colnames(outliers_exp_df)[i*2 - 1] = colnames(outliers_df)[i*2 - 1]
  colnames(outliers_exp_df)[i*2]     = paste(colnames(outliers_df)[i*2 - 1], "Expression")
  
  for(j in 1:length(na.omit(outliers_df[, 2*i -1]))){
    
    geneName = substring(outliers_df[j, 2*i -1], 1, nchar(outliers_df[j, 2*i -1]) -  4)
    
    outliers_exp_df[j, 2*i - 1] = geneName
    outliers_exp_df[j, 2*i]     = getOutlier_exp(cancerType, geneName)[['mean']]
    
  }
  
}

```

```{r}
# comparing outlier expression to baseline
expCompareGenes = function(cancerType, gene1, gene2){
  
  relevantCells = metadata[metadata$primary_disease == cancerType, 1]
  relevantCells = intersect(relevantCells, rownames(expression))
  relevantCells_exp = subset(expression, rownames(expression) %in% relevantCells)
  
  relevantCells_gene1 = relevantCells_exp[, c(gene1)]
  relevantCells_gene2 = relevantCells_exp[, c(gene2)]
  
  testResult = t.test(relevantCells_gene1, relevantCells_gene2)
  
  return(testResult)
  
}

expCompareToBaseline = function(cancerType, gene){
  
  relevantCells = metadata[metadata$primary_disease == cancerType, 1]
  relevantCells = intersect(relevantCells, rownames(expression))
  relevantCells_exp = subset(expression, rownames(expression) %in% relevantCells)
  
  relevantCells_gene = relevantCells_exp[, c(gene)]
  
  testResult = t.test(relevantCells_gene, unlist(relevantCells_exp))
  
  return(testResult)
  
}



```

```{r}
# plotting outlier expression
Outlier_Expression_Data_2 <- read_excel("~/Downloads/Outlier Expression Data-3.xlsx")
outlierExpression = Outlier_Expression_Data_2[!Outlier_Expression_Data_2$Talbe == "NA", ]
outlierExpression = na.omit(outlierExpression)
colnames(outlierExpression) = c("Gene", "Expression", "Cancer")

uniqueOutlierGenes = unique(outlierExpression[ ,1])

# mapping all genes per cancer
for(i in 1:15){
  
  cancerName = toString(top15Cancers$primary_disease[i])
  relevantGene_exp_df = outlierExpression[outlierExpression$Cancer == cancerName, ]
  relevantGene_exp_df$Expression = as.numeric(relevantGene_exp_df$Expression)
  
  p = ggplot(relevantGene_exp_df, aes(as.factor(Gene), Expression)) + geom_bar(stat = "identity") + labs(x = "Genes", y = "Expression Level", title = paste("Comparison of", cancerName, "and Outlier Gene Expression")) + scale_y_continuous(limits = c(0, 10)) + theme_bw() + theme(axis.text.x = element_text(angle = 90), panel.border = element_blank(), axis.line = element_line(colour = "black")) 
  print(p)
                                             
}

# mapping all cancers per gene
for(i in 1:18){
  
  geneName = toString(uniqueOutlierGenes[i, 1])
  relevantCancer_exp_df = outlierExpression[outlierExpression$Gene == geneName, ]
  relevantCancer_exp_df$Expression = as.numeric(relevantCancer_exp_df$Expression)
  
  p = ggplot(relevantCancer_exp_df, aes(as.factor(Cancer), Expression)) + geom_bar(stat = "identity") + labs(x = "Cancers", y = "Expression Level", title = paste("Comparison of", geneName, "Expression and Relevant Cancers")) + ylim(0,10) + theme_bw() + theme(axis.text.x = element_text(angle = 90), panel.border = element_blank(), axis.line = element_line(colour = "black")) 
  print(p)
                                       
}
  
# temp = count(outlierExpression$Cancer)
# freq = temp[temp$x == top15Cancers$primary_disease[i], ]
# freq = freq$freq

```

for(i in){
  
  for(j in 1:length(relevantGene_exp[1, ])){
    
    tempGeneName = relevantGene_exp[1, j]
    tempGene_exp = relevantGene_exp[2, j]
    
    
    
  }
}

specie = c(rep("Skin Cancer" , 11) , rep("Pancreatic Cancer" , 14) , rep("Ovarian Cancer" , 14) , rep("Neuroblastoma" , 14) , rep("Lymphoma" , 12) , rep("Lung Cancer" , 14) , rep("Colon/Colorectal Cancer" , 12) , rep("Head and Neck Cancer" , 10) , rep("Bone Cancer" , 11) , rep("Leukemia" , 14) , rep("Brain Cancer" , 13) , rep("Kidney Cancer" , 15) , rep("Gastric Cancer" , 14) , rep("Breast Cancer" , 12) , rep("Fibroblast" , 15) )# types of cancer

condition = rep(c("CSDC2" ,"FBXO48" ,"COL11A2" , "SS18L2" ,"STX5" ,"DYNLRB1" ,"RPA2" ,"USP10" ,"AURKA" ,"RCOR1" ,"RCOR1" ,"TAF1D" ,"OIP5" ,"BRF2" , "CDK6" , "LUC7L2", "LUC7L2", "UQCR11"), 15)

value = outlierExpression$Expression

ggplot(outlierExpression, aes(fill = condition, y = value, x = specie)) + geom_bar(position = "dodge", stat = "identity") + 
